\documentclass[12pt]{article}
\usepackage{booktabs,caption,geometry,amsmath,longtable,verbatim}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\geometry{margin=0.8in}
\captionsetup{labelsep=endash, font=normalsize, justification=centering}
\begin{document}

\begin{center}
{\Large\bfseries Anderson \& Sallee (2011)}\\
{\large Using Loopholes to Reveal the Marginal Cost of Regulation:}\\
{\large The Case of Fuel-Economy Standards}\\
\vspace{0.5em}
{\normalsize \textit{American Economic Review}, 101(4), 1375--1409}
\end{center}

\vspace{1em}
\noindent\textbf{Replication status:} Partial replication (CAFE compliance module only).
The proprietary transactions dataset (\texttt{transactions1.dta}) needed for
Tables 3--7 is unavailable. Tables 1, 2, and 8 plus Figures 1--5 are replicated
from the \texttt{cafe\_compliance.dta} dataset.

\tableofcontents

%% ====================================================================
\clearpage
\section{Table 1 -- Fuel Economy Performance and Flexible-Fuel Production}

Sales-weighted gallons-per-mile (GPM) averages by manufacturer and fleet type:
CAFE standard, AMFA-adjusted, and actual. Also reports total sales and FFV sales
by manufacturer and fleet. Output below is the raw Stata log; final table values
require additional calculations in Excel as noted by the authors.

\begin{scriptsize}
\verbatiminput{cafe_compliance_behavior.txt}
\end{scriptsize}

%% ====================================================================
\clearpage
\section{Table 8 -- Marginal Compliance Costs Per Vehicle}

Sales-weighted GPM for FFV vehicles and all vehicles by manufacturer, fleet, and year.
Corner-solution years are zeroed out. Final marginal cost calculations require
additional computations in Excel.

\begin{scriptsize}
\verbatiminput{cafe_compliance_costs.txt}
\end{scriptsize}

\end{document}
