\documentclass[12pt]{article}
\usepackage{booktabs,caption,geometry,amsmath,longtable,verbatim}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\geometry{margin=0.8in}
\captionsetup{labelsep=endash, font=normalsize, justification=centering}
\begin{document}

\begin{center}
{\Large\bfseries Handley \& Lima\~{o} (2017)}\\
{\large Policy Uncertainty, Trade, and Welfare:}\\
{\large Theory and Evidence for China and the United States}\\
\vspace{0.5em}
{\normalsize \textit{American Economic Review}, 107(9), 2731--2783}
\end{center}

\vspace{1em}
\noindent\textbf{Replication status:} Full replication. All data available.
6 main tables, 9 appendix tables, and 8 figures successfully replicated using Stata.

\tableofcontents

%% ====================================================================
\clearpage
\section{Table 1 -- Summary Statistics}

Summary statistics for key variables, split by low/high trade policy uncertainty.

\begin{small}
\verbatiminput{table1.csv}
\end{small}

%% ====================================================================
\clearpage
\section{Table 2 -- Baseline Import Growth Regressions}

OLS regressions of changes in log imports (2005--2000) on uncertainty, tariff changes,
and transport cost changes. Columns (1)--(2) without section dummies; (3)--(4) with section dummies.
Constrained specification restricts the uncertainty coefficient to match the NLS estimate.

\begin{small}
\verbatiminput{table2.out}
\end{small}

%% ====================================================================
\clearpage
\section{Table 3 -- Heterogeneity by Sunk Cost (Panel A)}

Import growth regressions split by terciles of sunk cost measures.
Panel A reports results for China and Taiwan separately, plus pooled specifications.

\begin{small}
\verbatiminput{table3_panelA.out}
\end{small}

\subsection*{Table 3 -- Panel B}

\begin{small}
\verbatiminput{table3_panelB.out}
\end{small}

%% ====================================================================
\clearpage
\section{Table 4 -- Price and Variety Decomposition}

Decomposition of import growth into price index changes and variety growth.
Columns (1)--(4) for prices, (5)--(8) for number of products.

\begin{small}
\verbatiminput{table4.out}
\end{small}

%% ====================================================================
\clearpage
\section{Table 5 -- Prices and Variety by Sunk Cost}

Price and variety regressions interacted with high/low sunk cost indicator.

\begin{small}
\verbatiminput{table5.out}
\end{small}

%% ====================================================================
\clearpage
\section{Table 6 -- NLS Structural Estimation}

Nonlinear least squares estimation of the structural model with the uncertainty
parameter $\alpha$ (sunk cost elasticity of trade). Compared with OLS reduced form.

\begin{small}
\verbatiminput{table6.out}
\end{small}

%% ====================================================================
%% APPENDIX TABLES
%% ====================================================================
\clearpage
\section{Appendix Table A1 -- Detailed Summary Statistics}

\begin{small}
\verbatiminput{tableA1.csv}
\end{small}

%% ====================================================================
\clearpage
\section{Appendix Table A2}

\begin{small}
\verbatiminput{tableA2.out}
\end{small}

%% ====================================================================
\clearpage
\section{Appendix Table A3 -- Panel A}

\begin{small}
\verbatiminput{tableA3_panelA.out}
\end{small}

\subsection*{Appendix Table A3 -- Panel B}

\begin{small}
\verbatiminput{tableA3_panelB.out}
\end{small}

%% ====================================================================
\clearpage
\section{Appendix Table A4}

\begin{small}
\verbatiminput{tableA4.out}
\end{small}

%% ====================================================================
\clearpage
\section{Appendix Table A5}

\begin{small}
\verbatiminput{tableA5.out}
\end{small}

%% ====================================================================
\clearpage
\section{Appendix Table A6}

\begin{small}
\verbatiminput{tableA6.out}
\end{small}

%% ====================================================================
\clearpage
\section{Appendix Table A7}

\begin{small}
\verbatiminput{tableA7.out}
\end{small}

%% ====================================================================
\clearpage
\section{Appendix Table A8}

\begin{small}
\verbatiminput{tableA8.out}
\end{small}

%% ====================================================================
\clearpage
\section{Appendix Table A9}

\begin{small}
\verbatiminput{tableA9.out}
\end{small}

\end{document}
