\documentclass[12pt]{article}
\usepackage{booktabs,caption,geometry,amsmath,longtable,verbatim}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\geometry{margin=0.8in}
\captionsetup{labelsep=endash, font=normalsize, justification=centering}
\begin{document}

\begin{center}
{\Large\bfseries Bloom, Sadun \& Van Reenen (2012)}\\
{\large The Organization of Firms Across Countries}\\
\vspace{0.5em}
{\normalsize \textit{Quarterly Journal of Economics}, 127(4), 1663--1705}
\end{center}

\vspace{1em}
\noindent\textbf{Replication status:} Partial replication (European data only).
The UK establishment-level data required for Tables 1--5 and Table C1 is unavailable
(restricted access). Tables 6, C2, A5, and A6 are replicated from the European
cross-country survey data (\texttt{replicate.dta}).

\tableofcontents

%% ====================================================================
\clearpage
\section{Table 6 -- Decentralization and Firm Characteristics (European Data)}

OLS regressions of decentralization on firm characteristics across European countries.
Dependent variable: log of plant-level autonomy index (\texttt{ly}) in columns (1)--(6),
log of PCs per employee (\texttt{lpcemp}) in columns (7)--(8).
Key regressors include log capital (\texttt{lcap}), log employment (\texttt{lemp}),
US and other multinational dummies, log PCs per employee and interactions,
trust (\texttt{ldegree\_t}), and people skills (\texttt{peeps}).

\begin{small}
\verbatiminput{Table6.csv}
\end{small}

%% ====================================================================
\clearpage
\section{Table C2 -- Management Practices and Decentralization}

Robustness checks replacing the aggregate people skills variable with specific
management practice sub-indices: operations, monitoring, targets, and overall management.

\begin{small}
\verbatiminput{tablec2.csv}
\end{small}

%% ====================================================================
\clearpage
\section{Table A5 -- Selection into Interview (All Firms)}

Probit/OLS regressions testing whether observable firm characteristics predict
interview completion. Dependent variable: indicator for completing the survey interview.

\begin{small}
\verbatiminput{TableA5.csv}
\end{small}

%% ====================================================================
\clearpage
\section{Table A6 -- Selection into Matching (Matched Sample)}

Regressions testing whether observable characteristics predict successful matching
to accounting data among interviewed firms.

\begin{small}
\verbatiminput{TableA6.csv}
\end{small}

\end{document}
